---
title: "Lab 01 - Hello R"
author: "Ryan W"
date: "2/6/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(datasauRus)
```

## Exercises

### Exercise 1

datasaurus_dozen has:
1846 rows,
3 variables,
but I don't see anywhere in the help where it says the number of columns

### Exercise 2 -- completed

The answers for this exercise are given for you below.
But you should clean up some of the narrative so that it only includes what you want to turn in.

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-star}

star_data %>%
  summarize(r = cor(x, y))
```
This is almost the same correlation as the dinosaur data.

### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.



## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
